% File name     : Work_Experience2.tex
% Description   : It places the "Work_Experience2" CVSection in this script
% Author        : Frederique Hsu
% Date          : Sun.  13 Oct. 2024
%
%


\documentclass[./CV]{subfiles}


\begin{document}
    
    {\zihao{6}{
    \begin{itemize}
        \item \underline{RoadTrackerModule} computes out the curved shape and boundary of road.

        \item \underline{TrajectoryTrackerModule} calcuates the movement trajectory of each vehicle by using the Kalmann Filter algorithm, according to the position, 
        
        direction and status of surrounding vehicles, which are relative to EgoVehicle, at every time slot. What's more, save these trajectories and update them.
    
        \item \underline{ClusteringModule} adopts the Kruskal/Prim algorithms to classify the trajectories and aggregate into Left/Ego/Right 3 bunches.
        
        \item \underline{CenterFusionModule} is responsible to fusion out the Ego lane, which will be used to guide the EgoVehicle.
        
        \item \underline{LaneFinderModule} and \underline{LanTrackerModule} then extracts the stable lanes from the trajectory bunches, and track/update the 
        lanes in real-time.
    \end{itemize}
    }}

    \cvdetail{
        Implement the Lane Fusion \& Path Guidance feature based on Tencent SD/HD map, splice the lane segments on the map together to form the legal
        
        driving path via the shortest path algorithm, then guide the EgoVehicle to drive along this path, including ramp up/down.
    }
    
    \cvdetail{
        Fix the software issues of Road Model module, write some sufficient test cases, maintain the Docker container auto-testing pipeline in data
        
        center, and take part in the prototype vehicle AD testing in Deqing testing ground and Shandong Highway to validate the software functionalities.
    }
    
    \vspace{10pt}
    \textcolor{blue!30}{\hrule}
    \engcvsubsection{Jun. 2020 - Mar. 2022}{Senior C++ development engineer}{MicroPort MedBot Surgical Robot}
    
    \cvdetail{
        Developed the 1st domestic laparoscopic surgical robot: Toumai.  I took part in the development of 4 core modules as below:
        This system adopts the PLC ST(another kind of OOP language, 
        \begin{tabular}{|l|l|l|l|}
            \hline
            LogicControl & MotionControl & RobotKinematics & ForceControl \\
            \hline
        \end{tabular}
        but it features the hardware real-time as PLC) and C++ hybrid programming, based on Beckhoff TwinCAT platform, we've achieved the 
        real-time manipulation from the master 2 arms on the surgeon cart to the slave 4 arms on the patient cart.
        
        Besides the development, we have collaborated with the surgeons from Shanghai Changhai hospital and SAHZU hospital to carry out the 
        pancreatectomy, radical prostatectomy and hysteromyomectomy experiments on pigs and corpses, in order to validate its clinical 
        applicability. Toumai finally passed the model certificate of NMPA on Jan. 27, 2022, as the sole domestic surgical robot.
    }
    
    \cvdetail{
        Developed the software system of Toumai surgical robot patient cart independently, I had adopted Qt QML to render the fancy and surgeon-
        friendly HMI, designed a well-organized architecture with 4-hierarchical layers: ControlUI---HMI logic---ADS Comm.---MotionCtrl, plus one 
        independent Error Management module.
        
        I also proposed/implemented the innovative real-time mapping mechanism between State-Machine on driver layer and Mirror-State-Machine on 
        UI application layer. This state-of-the-art software architecture realized the real-time response/control effect on both hardware and 
        software. I used Qt QML/C++/Windows Driver hybrid programming to develop the software system.
    }
    
    \vspace{10pt}
    \textcolor{blue!30}{\hrule}
    \engcvsubsection{Aug. 2016 - May 2020}{Software engineer}{Shanghai Amphenol Airwave}
    
    \cvdetail{
        During the period I worked in SAA, I have accomplished these important projects as below:
        \begin{center}
            \begin{tabular}{c|p{19cm}}
                \hline
                \multirowcell{8}{1} & 
                Developed a comprehensive software platform and management suite in C\# and C++:
                \href{https://github.com/Frederick-Hsu/AUPS}{AUPS (Augmented Universal Platform \& Sequenzer)}
                
                It builds an integrated platform to support general-purpose automatic function testing, manages
                and executes the testing flow for communication electronic product. It also offers engineers the
                2nd development for customization capability (This project had opened in GitHub.)
                
                \faCaretRight\quad{}AUPS utilizes the sequence.xml test script to save and organize test items, manages
                their automation flow, provides the graphical editor to allow editing items and parameters by engineers themself.
                
                \faCaretRight\quad{}Design an uniform UI to monitor the automatic testing process.
                
                \faCaretRight\quad{}AUPS achieved up to 16 sessions running in parallel, multiple instruments can be connected together
                over the ethernet, to compose the auto-testing production line, AUPS facilitated to improve automation dramatically.
                \\
                \hline
                \multirowcell{2}{2} &
                Wrote out a set of class library to access various instruments, as long as the instruments support VISA standard, 
                which covers a wide range of instrument models from Keysight, R\&S and Tektronix etc.
                \\
                \hline
                \multirowcell{2}{3} &
                Designed the NFC data link equipment for programming firmware image to \faApple{} iPhone 8 \& X smart phones in the 
                contactless way. 
                
                We had applied a patent for this equipment: One kind of NFC data transferring device with ultra-large capability.
                \\
                \hline
                \multirowcell{2}{4} &
                Based on the AUPS software, I developed a suite of integrated utility, to help GM's Chevrolet, Cadillac SUV to carry out
                the automatic testing about V2X vehicle communication, and traveled to Detroit GM tech. center to guide the testing and
                development.\\
                \hline
            \end{tabular}
        \end{center}
    }
    
    \vspace{10pt}
    \textcolor{blue!30}{\hrule}
    \engcvsubsection{Feb. 2012 - Jun. 2016}{Senior software dev./testing engineer}{Hella Shanghai Electronics}
    
    \cvdetail{
        Developed the production automatic testing system and equipment, based on NI LabWindows/CVI(pure ANSI C), including testing
        software development, hardware controlling system design and integration . 
        I had accomplished the following important testing system projects as below:
        
        \begin{tabular}{l}
            \faCaretRight\quad{}Peugeot-Citro\"{e}n RKE remote key testing system \\
            \faCaretRight\quad{}Volkswagen FKS12 \& Kessy passive entry passive start product testing equipment \\
            \faCaretRight\quad{}BMW \& MINI remote key (both RKE and PEPS PKE) automatic testing system \\
            \faCaretRight\quad{}The Insulation Monitoring Device testing system development for Mercedes-Benz \& BYD jointed DENZA battery-electric-vehicle \\
        \end{tabular}
    }
    
    \cvdetail{
        Developed a compact integrated test instruments DCU, in order to replace the expensive NI PXI-card instruments. Based on Renesas V850 uPD70F3376 MCU, 
        I wrote only by myself the \href{https://github.com/Frederick-Hsu/DCU_MCTBox_Firmware}{DCU\_MCTBox\_Firmware}, 
        \href{https://github.com/Frederick-Hsu/DCU_MCTBox_API}{DCU\_MCTBox\_API} and 
        \href{https://github.com/Frederick-Hsu/DCU_MCTBox_Diagnoser}{DCU\_MCTBox\_Diagnoser} utility software. 
        This DCU provides such functions as SwitchMatrix, DIO, DigitMeter, DigitVoltSource, CAN/LIN analyzer etc., which can meet the basic requirement of 
        automotive electronics product. 
        
        This project had fully opened in GitHub, expect that developing the open-source, cheap but standard-shared testing instruments
        with open community.
    }
    
    \vspace{10pt}
    \textcolor{blue!30}{\hrule}
    \engcvsubsection{Oct. 2009 - Feb. 2012}{Test software engineer}{Shanghai Foxconn}
    
    \vspace{10pt}
    \textcolor{blue!30}{\hrule}
    \engcvsubsection{Jul. 2006 - Aug. 2009}{LCD TV firmware engineer}{TPV AOC (Fuzhou)}
\end{document}